---
title: "A Globally-Sourced Collection"
output: 
  flexdashboard::flex_dashboard:
    orientation: column
    vertical_layout: fill
    navbar:
      - {icon: "fa-home", href: "./index.html", align: right }
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(leaflet)
library(sf)
library(rnaturalearth)
library(rsconnect)
library(wesanderson)  
library(viridis)
library(wesanderson)
library(dplyr)
library(RColorBrewer)
```

```{r, echo=FALSE, warning=FALSE}
load("data/met.RData")
```

```{r, echo=FALSE}
met_country <- met |> 
mutate(country = case_when(
    country == "Central Turkey" ~ "Turkey",
    country == "USA" ~ "United States", 
    country == "Iran(Persia)" ~ "Iran", 
    country == "Ivory Coast" ~ "Cote d'Ivoire", 
    country == "iran" ~ "Iran", 
    country == "Eastern India" ~ "India",
    country == "Byzantine Egypt" ~ "Egypt",
    country == "Western Australia" ~ "Australia",
    country == "England" ~ "United Kingdom",
    country == "England|England" ~ "United Kingdom",
    country == "Croatia (former Yugoslavia)" ~"Crotia",
    country == "Western France" ~ "France", 
    country == "Southern Netherlands" ~ "Netherlands",
    country == "Southern Netherland" ~ "Netherlands", 
    country == "Scotland" ~ "United Kingdom",
    country == "Republic of Congo" ~ "Congo", 
    country == "Republic of Cameroon" ~ "Cameroon",
    country == "Republic of Costa Rica" ~ "Costa Rica",
    country == "Republic of Guinea-Bissau" ~ "Guinea-Bissau",
    country == "Republic of the Marshall Islands" ~ "Marshall Isl",
    country == "Republic of Guinea-Bissau" ~ "Guinea-Bissau",
    country == "Republic of Benin" ~ "Benin",
    country == "Czech Republic" ~ "Czech Rep.",
    country == "Northern Iran"  ~"Iran",
    country == "Northwestern Iran"  ~"Iran",
    country == "Northwest Iran"  ~"Iran",
    country == "Northwestern Iran" ~"Iran",
    country == "Northern India" ~ "India",
    country == "Nothern France" ~ "France", 
    country == "Cook Islands" ~ "Cook Is.",
    country == "Democratic Republic of the Congo" ~ "Dem. Rep. Congo", 
    country == "Gemany" ~ "Germany",
    country == "Myanmar (formerly Burma)" ~ "Mynmar",
    country == "New Guinea" ~ "Papua New Guinea", 
    country == "Republic of  Cameroon" ~ "Cameroon",
    country == "United States|United States" ~ "United States", 
    country == "Costa Rica|Costa Rica" ~"Costa Rica",
    country == "Burkina Faso (formerly Upper Volta)" ~ "Burkina Faso",
    country == "Unknown" ~ "NA",
    TRUE ~ as.character(country)
  ), 
  country = str_replace(country, "present-day ", ""))

```

```{r, echo=FALSE, message=FALSE}
object_counts <- met_country |> 
  group_by(country, object_name) |> 
  summarise(n_objects = n()) |> 
  group_by(country) |> 
  summarise(total_objects = sum(n_objects, na.rm = TRUE)) 

world <- ne_countries(scale = "medium", returnclass = "sf")

world_df <- left_join(world, object_counts, by = c("name" = "country"))
world2 <- left_join(object_counts, world, by = c("country" = "name"))

world2 <- world2 |> 
  filter(is.na(scalerank))
```


Column {data-width=60%}
-----------------------------------------------------------------------

### Where Met Objects Originate

```{r, echo= FALSE, warning=FALSE, message=FALSE}

world_df <- st_transform(world_df, 4326)

pal <- colorNumeric(
  palette = "YlOrRd", 
  domain = world_df$total_objects,
  na.color = "transparent"
)
world_df <- st_transform(world_df, 4326)

wes_anderson_palette <- c("#8FBEDC", "#F4D6A1", "#D7C9A7", "#D16E5A", "#B3CC57")

map <- leaflet(world_df, width = "50%", height = "50%") |>
  setView(lng = 0, lat = 0, zoom = 2) |>
  addTiles() |> 
  addPolygons(
    fillColor = ~pal(total_objects),
    weight = 1,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.8,
    highlight = highlightOptions(
      weight = 2,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE
    ),
    label = ~paste(name, ": ", total_objects)
  )  |> 
  addLegend(
    "bottomright",
    title = "Total Objects",
    pal = colorNumeric(palette = wes_anderson_palette, domain = world_df$total_objects, na.color = "transparent"),
    values = ~total_objects,
    opacity = 0.7
  )

map



```
 


Row {data-width=40%}
-----------------------------------------------------------------------

### Top 20 Countries by Number of Objects


```{r, echo=FALSE, warning=FALSE, message=FALSE}

top_countries <- object_counts |> 
  arrange(desc(total_objects)) |> 
  head(20)

# Set a color palette
palette <- brewer.pal(20, "YlOrRd")

# Use colorNumeric to create a color palette based on total_objects
color_palette <- colorNumeric(
  palette = palette,
  domain = top_countries$total_objects,
  na.color = "transparent"
)

# Create the plot
plot_ly(
  data = top_countries, 
  x = ~country, 
  y = ~total_objects, 
  type = "bar",
  marker = list(color = ~color_palette(total_objects))
) |> 
  add_text(
    text = ~total_objects,
    position = "top",
    showlegend = FALSE
  ) |> 
  layout(
    xaxis = list(categoryorder = "total ascending"),
    yaxis = list(title = "# of Objects"),
    showlegend = FALSE  # Hide legend if desired
  )

```
 


### Objects Not Attributed to a Specific Country


```{r, echo=FALSE, warning=FALSE, message=FALSE}
world2 <- world2 %>%
  mutate(
    category = case_when(
      grepl("or|probably|\\?", tolower(country)) ~ "Uncertain",
      grepl("\\|,| and", country) ~ "Multiple Countries",
      grepl(",", country) ~ "Multiple Countries",
      grepl("and", country) ~ "Multiple Countries",
      TRUE ~ "Other"
    )
  )

world2 <- world2 |> 
  count(category)

wes_palette <- wes_palette("Moonrise2", n = 3)


plot_ly(
  data = world2,
  x = ~category,
  y = ~n,  # 'n' is the count column created by count
  type = 'bar',
  marker = list(color = wes_palette, line = list(color = 'black'))
) |> 
  layout(
    xaxis = list(title = "Non-descript Country Source Category"),
    yaxis = list(title = "Total")
  )


```


### Global Origins of Met Objects

You are inside the Met and enjoying your trip. You go from one department to another. Soon, you realize you've spent an exceptionally long time in the Egyptian Art section, and there are still rooms to go. How big is this place? You start to get a sense that everything in the museum might come from Egypt. Well, you're almost right! Compared to other countries, Egypt does blow the rest out of the water when it comes to counting the number of works originated to each location. The United States takes second place on the podium, while Iran takes third place. 

But wait! Now, you might be wondering how the Met keeps track of the origin of each item. Surely, it must be challenging for Met employees to document the details of every item over the years. Perhaps, in some cases, the location of certain items was never determined from the beginning. And you're correct! The location of 93 items in the Met collection is uncertain, indicating that these items were recorded as being from two or three countries, or the experts were unsure about the specific country, providing multiple possibilities. For instance, some items are recorded as being from Afghanistan or Iran, and some are recorded as possibly from Syria. Additionally, there are items recorded as belonging to two countries, reflecting the historical changes in borders over the years. 

Notably, there's a large pool of 40,840 items in the Met's collection which have no location information whatsoever, as their country data is simply listed as "Not Available." 