---
title: "c_exhibit_b_the_art.html"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
---

# Exploring the Met's Departments

```{r include = FALSE}
library(tidyverse)
library(plotly)

load("data/met.RData")

mypal = c("#78B7C5",  "#EBCC2A", "#FF0000", "#EABE94", 
         "#3B9AB2", "#B40F20", "#0B775E", "#F2300F", 
         "#5BBCD6", "#F98400", "#ab0213", "#E2D200", 
         "#ff7700", "#46ACC8", "#00A08A", "#78B7C5",
         "#a7ba42", "#f94f8a", "#DD8D29")
```

```{r echo = FALSE}
met |>
  count(department) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  select(department, n) |> 
  rename("Department" = department, "Number of Objects" = n) |>
  knitr::kable()
```

The most objects can be found in the following departments: 1) Drawings and Prints; 2) European Sculpture and Decorative Arts; and 3) Asian Art.

Explore each department and the number of objects they hold! 

```{r echo = FALSE}
met |> 
  count(department) |> 
  mutate(department = fct_reorder(department, n)) |> 
  plot_ly(x = ~department, y = ~n, color = ~department, type = "bar", colors = mypal) |>
  layout(xaxis = list(title = 'Department'), 
         yaxis = list(title = 'Number of Objects'),
         legend = list(title = list(text ='Department')))
```

Objects by Department

* Drawings and Prints

```{r echo = FALSE}
met |>
  filter(department == "Drawings and Prints") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* European Sculpture and Decorative Arts

```{r echo = FALSE}
met |>
  filter(department == "European Sculpture and Decorative Arts") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* Photographs

```{r echo = FALSE}
met |>
  filter(department == "Photographs") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* Asian Art

```{r echo = FALSE}
met |>
  filter(department == "Asian Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* Greek and Roman Art

```{r echo = FALSE}
met |>
  filter(department == "Greek and Roman Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* Costume Institue

```{r echo = FALSE}
met |>
  filter(department == "Costume Institute") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* Egyptian Art

```{r echo = FALSE}
met |>
  filter(department == "Egyptian Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* The American Wing

```{r echo = FALSE}
met |>
  filter(department == "The American Wing") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* Islamic Art

```{r echo = FALSE}
met |>
  filter(department == "Islamic Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* Modern and Contemporary Art

```{r echo = FALSE}
met |>
  filter(department == "Modern and Contemporary Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* Arms and Armor

```{r echo = FALSE}
met |>
  filter(department == "Arms and Armor") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* Arts of Africa, Oceania, and the Americas

```{r echo = FALSE}
met |>
  filter(department == "Arts of Africa, Oceania, and the Americas") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* Medieval Art

```{r echo = FALSE}
met |>
  filter(department == "Medieval Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* Ancient Near Eastern Art

```{r echo = FALSE}
met |>
  filter(department == "Ancient Near Eastern Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* Musical Instruments

```{r echo = FALSE}
met |>
  filter(department == "Musical Instruments") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* European Paintings

```{r echo = FALSE}
met |>
  filter(department == "European Paintings") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* Robert Lehman Collection

```{r echo = FALSE}
met |>
  filter(department == "Robert Lehman Collection") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```

* The Cloisters

```{r echo = FALSE}
met |>
  filter(department == "The Cloisters") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable()
```


