---
title: "Subsetting and Saving Data"
author: "Aleya Khalifa"
date: "`r Sys.Date()`"
output: html_document
---

```{r, include = FALSE}
library(tidyverse)
library(readr)
```

## Import data

```{r}
met <- read_delim("data/MetObjectsTxt.txt") %>%  
  janitor::clean_names()
```


### Check missingness

The variable `accession_year` has high completeness. And `culture` has moderate completeness. Here is a table of the % rows with missing values by selected column:

```{r}
sapply(met, function(x) sum(is.na(x))/nrow(met))
```


### Clean up object types to create more general classes

Note that the `object_name` variable can be more detailed than is necessary. Here, I try to create more general categories of objects.

```{r}
met <- met %>%
  mutate(object_name = ifelse(
    grepl("Textile", object_name), "Textile",
    ifelse(grepl("Painting", object_name), "Painting",
    ifelse(grepl("Relief", object_name), "Relief",
    ifelse(grepl("Print", object_name), "Print", 
           ifelse(grepl("aseball card", object_name), "Baseball card", 
                  ifelse(grepl("Vase", object_name), "Vase", 
                         ifelse(grepl("rnament", object_name), "Vase", 
                                ifelse(grepl("arring", object_name), "Earring", 
                                       ifelse(grepl("ecklace", object_name), "Necklace", 
                                              ifelse(grepl("hotograph", object_name), "Photograph", 
                                                     ifelse(grepl("tatue", object_name), "Statue", 
           object_name))))))))))))
```

## Examine different subsets

| Subset scenario                                                                              | Number of rows                                                                                         | Notes                                  |
|---------------------------------------|-----------------|------------------|
| Random 10% sample                                                                            | `r nrow(sample_n(met,nrow(met)*.10))`                                                                  |                                        |
| Observations with complete data for `object_name` and `accession_year`                       | `r nrow(filter(met,!is.na(object_name) & !is.na(accession_year)))`                                     |                                        |
| Random 10% of sample with complete data for `object_name` and `accession_year`               | `r nrow(sample_n(filter(met,!is.na(object_name) & !is.na(accession_year)),nrow(met)*.10))`             | Might be best                          |
| Observations with complete data for `object_name` , `accession_year` , `culture`             | `r nrow(filter(met,!is.na(object_name) & !is.na(accession_year) & !is.na(culture)))`                   | Different picture of objects over time |
| Observations with complete data for `object_name` , `accession_year` , `culture` , `country` | `r nrow(filter(met,!is.na(object_name) & !is.na(accession_year) & !is.na(culture) & !is.na(country)))` | Different picture of objects over time |

: Subsetting scenarios

## Save R data file

Chosen subset: Random 10% of sample with complete data for `object_name` and `accession_year` 

```{r}
met <- met %>%
  filter(!is.na(object_name) & !is.na(accession_year)) %>%
  sample_n(nrow(met)*.10)
  
save(met, 
     file = "data/met.RData")
```
