---
title: "Subsetting and Saving Data"
author: "Aleya Khalifa"
date: "`r Sys.Date()`"
output: html_document
---

```{r, include = FALSE}
library(tidyverse)
```

## Import data

Note: `met_10` is a random sample of 10% of The Met's original dataset _MetObjects_, which comes in a text file. Here, we clean up the dataset a bit before using it in analysis. The cleaned dataset is named `met`.

```{r}
load("met_10.RData")

met <- met_10 %>%  
  janitor::clean_names()
```


### Check missingness

The variable `accession_year` has high completeness. And `culture` has moderate completeness. Here is a table of the % rows with missing values by selected column:

```{r}
sapply(met, function(x) sum(is.na(x))/nrow(met))
```


### Clean up object types to create more general classes

Note that the `object_name` variable can be more detailed than is necessary. Here, I try to create more general categories of objects.

```{r}
met <- met %>%
  mutate(object_name = ifelse(
    grepl("Textile", object_name), "Textile",
    ifelse(grepl("Painting", object_name), "Painting",
    ifelse(grepl("Relief", object_name), "Relief",
    ifelse(grepl("Print", object_name), "Print", 
           ifelse(grepl("aseball card", object_name), "Baseball card", 
                  ifelse(grepl("Vase", object_name), "Vase", 
                         ifelse(grepl("rnament", object_name), "Vase", 
                                ifelse(grepl("arring", object_name), "Earring", 
                                       ifelse(grepl("ecklace", object_name), "Necklace", 
                                              ifelse(grepl("hotograph", object_name), "Photograph", 
                                                     ifelse(grepl("tatue", object_name), "Statue", 
           object_name))))))))))))
```


## Save R data file

Chosen subset: Objects with complete data for `object_name` and `accession_year` - two crucial variables for our analysis.

```{r}
met <- met %>%
  filter(!is.na(object_name) & !is.na(accession_year)) 
  
save(met, 
     file = "data/met.RData")
```
