---
title: "Exhibition B: Exploring the Met's Departments"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    code_folding: hide
---

```{r include = FALSE}
library(tidyverse)
library(plotly)

load("data/met.RData")

mypal = c("#78B7C5",  "#EBCC2A", "#FF0000", "#EABE94", 
         "#3B9AB2", "#B40F20", "#0B775E", "#F2300F", 
         "#5BBCD6", "#F98400", "#ab0213", "#E2D200", 
         "#ff7700", "#46ACC8", "#00A08A", "#78B7C5",
         "#a7ba42", "#f94f8a", "#DD8D29")
```

# **Departments**

The Met holds many collections from Modern and Contemporary Art to Arms and Armor. 
Explore the vast departments of the Met and the many objects they contain. Explore the different kinds of objects that each department holds. Click [here](https://www.metmuseum.org/about-the-met/collection-areas) to learn more about each department, or collection area.

```{r}
met |>
  count(department) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  select(department, n) |> 
  rename("Department" = department, "Number of Objects" = n) |>
  knitr::kable(caption = "Top 3 Departments by Number of Objects")
```

```{r}
met |> 
  count(department) |> 
  mutate(department = fct_reorder(department, n)) |> 
  plot_ly(x = ~department, y = ~n, color = ~department, type = "bar", colors = mypal) |>
  layout(title = 'Explore each department and their number of objects',
         xaxis = list(title = 'Department'), 
         yaxis = list(title = 'Number of Objects'),
         legend = list(title = list(text ='Department')))
```

The most objects can be found in the following departments: 1) Drawings and Prints; 2) European Sculpture and Decorative Arts; and 3) Asian Art.

```{r}
met |>
  filter(is_highlight == TRUE) |>
  count(department) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  select(department, n) |> 
  rename("Department" = department, "Number of Highlighted Objects" = n) |>
  knitr::kable(caption = "Top 3 Departments by Number of Highlighted Objects")
```

```{r}
met |> 
  filter(is_highlight == TRUE) |>
  count(department) |> 
  mutate(department = fct_reorder(department, n)) |> 
  plot_ly(x = ~department, y = ~n, color = ~department, type = "bar", colors = mypal) |>
  layout(xaxis = list(title = 'Department'), 
         yaxis = list(title = 'Number of Highlighted Objects'),
         legend = list(title = list(text ='Department')))
```

The most highlighted objects can be found in the following departments: 1) The American Wing; 2) Asian Art; and 3) Costume Institute.

## Drawings and Prints

```{r}
met |>
  filter(department == "Drawings and Prints") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Drawings and Prints") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal,
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 740))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In Drawings and Prints, the most common objects are: 1) Print; 2) Drawing; and 3) Book.

## European Sculpture and Decorative Arts

```{r}
met |>
  filter(department == "European Sculpture and Decorative Arts") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "European Sculpture and Decorative Arts") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal,
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 89))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In European Sculpture and Decorative Arts, the most common objects are: 1) Piece; 2) Fragment; and 3) Vase.

## Photographs

```{r}
met |>
  filter(department == "Photographs") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Photographs") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal,
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 80))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In Photographs, the most common objects are: 1) Photograph; 2) Negative; and 3) Carte-de-visite.

## Asian Art

```{r}
met |>
  filter(department == "Asian Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Asian Art") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal,
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 130))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In Asian Art, the most common objects are: 1) Piece; 2) Print; and 3) Vase.

## Greek and Roman Art

```{r}
met |>
  filter(department == "Greek and Roman Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Greek and Roman Art") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal,
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 100))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In Greek and Roman Art, the most common objects are: 1) Kylix fragment; 2) Statue; and 3) Vase.

## Costume Institue

```{r}
met |>
  filter(department == "Costume Institute") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Costume Institute") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal,
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 90))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In Costume Institute, the most common objects are 1) Dress; 2) Ensemble; and 3) Evening dress.

## Egyptian Art

```{r}
met |>
  filter(department == "Egyptian Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Egyptian Art") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal,
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 62))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In Egyptian Art, the most common objects are: 1) Relief; 2) Scarab; and 3) Jar Label.

## The American Wing

```{r}
met |>
  filter(department == "The American Wing") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "The American Wing") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal,
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 59))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In The American Wing, the most common objects are: 1) Drawing; 2) Painting; and 3) Watercolor.

## Islamic Art

```{r}
met |>
  filter(department == "Islamic Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Islamic Art") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal,
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 42))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In Islamic Art, the most common objects are: 1) Fragment; 2) Textile; and 3) Coin.

## Modern and Contemporary Art

```{r}
met |>
  filter(department == "Modern and Contemporary Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Modern and Contemporary Art") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal, 
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 80))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In Modern and Contemporary Art, the most common objects are: 1) Drawing; 2) Painting; and 3) Textile.

## Arms and Armor

```{r}
met |>
  filter(department == "Arms and Armor") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Arms and Armor") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal,
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 25))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In Arms and Armor, the most common objects are: 1) Sword guard (Tsuba); 2) Knife handle (Kozuka); and 3) Arrowhead (Yanone).

## Arts of Africa, Oceania, and the Americas

```{r}
met |>
  filter(department == "Arts of Africa, Oceania, and the Americas") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Arts of Africa, Oceania, and the Americas") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal,
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 35))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In Arts of Africa, Oceania, and the Americas, the most common objects are: 1) Vase; 2) Figure; and 3) Mask.

## Medieval Art

```{r}
met |>
  filter(department == "Medieval Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Medieval Art") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal,
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 24))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In Medieval Art, the most common objects are: 1) Fragment; 2) Ostrakon; and 3) Brooch.

## Ancient Near Eastern Art

```{r}
met |>
  filter(department == "Ancient Near Eastern Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Ancient Near Eastern Art") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal,
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 30))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In Ancient Near Eastern Art, the most common objects are: 1) Stamp seal; 2) Cuneiform tablet; and 3) Cylinder seal.

## Musical Instruments

```{r}
met |>
  filter(department == "Musical Instruments") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Musical Instruments") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal,
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 8))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In Musical Instruments, the most common objects are: 1) Bell; 2) Pottery Whistle; and 3) Rattle.

## European Paintings

```{r}
met |>
  filter(department == "European Paintings") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "European Paintings") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In European Paintings, the most common objects are: 1) Painting; and 2) Drawing.

## Robert Lehman Collection

```{r}
met |>
  filter(department == "Robert Lehman Collection") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Robert Lehman Collection") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal,
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 6))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In the Robert Lehman Collection, the most common objects are: 1) Drawing; 2) Frame; and 3) Painting.

## The Cloisters

```{r}
met |>
  filter(department == "The Cloisters") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "The Cloisters") |>
  count(object_name) |> 
  mutate(object_name = fct_reorder(object_name, n)) |> 
  plot_ly(x = ~object_name, y = ~n, color = ~object_name, type = "bar", colors = mypal,
          transforms = list(
          list(
          type = 'filter',
          target = 'y',
          operation = '>',
          value = 10))) |>
  layout(title = 'Explore the Objects',
         xaxis = list(title = 'Object Name'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

In The Cloisters, the most common objects are: 1) Panel, 2) Pilgrim's badge; and 3) Capital.
