---
title: "Exhibition B: Exploring the Met's Departments"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    code_folding: hide
---

```{r include = FALSE}
library(tidyverse)
library(plotly)
library(wesanderson)


load("data/met.RData")

mypal = c("#78B7C5",  "#EBCC2A", "#FF0000", "#EABE94", 
         "#3B9AB2", "#B40F20", "#0B775E", "#F2300F", 
         "#5BBCD6", "#F98400", "#ab0213", "#E2D200", 
         "#ff7700", "#46ACC8", "#00A08A", "#78B7C5",
         "#a7ba42", "#f94f8a", "#DD8D29")

theme_set(theme_minimal())
```

# Departments

The Met holds many collections from Modern and Contemporary Art to Arms and Armor. 
Explore the vast departments of the Met and the many objects they contain. Explore the different kinds of objects that each department holds. Click [here](https://www.metmuseum.org/about-the-met/collection-areas) to learn more about each department, or collection area.

The department with the most objects is [Drawings and Prints](https://www.metmuseum.org/about-the-met/collection-areas/drawings-and-prints) with 4 times as many objects as the next department! (Interestingly enough, works on paper can only be in exhibition ~3 months at a time due to their fragility.) Yet that changes when looking at the most highlighted objects, or popular pieces of artwork, as the department with the most highlighted number of objects is [The American Wing](https://www.metmuseum.org/about-the-met/collection-areas/the-american-wing). Close behind The American Wing, Asian Art comes in second with the most highlighted objects.

As we explore each department and the objects they hold, we find that Drawings and Prints mostly contains drawings and prints (no surprise there). In Drawings and Prints, prints has more than triple the number of objects than the other objects. [Photographs](https://www.metmuseum.org/about-the-met/collection-areas/photographs) also mainly contains photographs (again, not shocking and 3 times the number of objects compared to the other objects). The most common object was a piece in both [Asian Art](https://www.metmuseum.org/about-the-met/collection-areas/asian-art) and [European Sculpture and Decorative Arts](https://www.metmuseum.org/about-the-met/collection-areas/european-sculpture-and-decorative-arts). 

Unlike any other department, [Greek and Roman Art](https://www.metmuseum.org/about-the-met/collection-areas/greek-and-roman-art) mostly contains Kylix fragments (nearly 8 times any other object!). Kylix fragments, or vessels, are specific to Greek and Roman culture. Again, unlike any other department, the [Egyptian Art](https://www.metmuseum.org/about-the-met/collection-areas/egyptian-art) department has objects like reliefs, or painted scenes, and scarabs, or beetle shaped amulets. We explored the Egyptian Art department further [here](https://lakerss12.shinyapps.io/shiny_app/). 

Finally, let's discuss a collection close to us at CUMC: [The Cloisters](https://www.metmuseum.org/about-the-met/collection-areas/medieval-art-and-the-cloisters). This collection mostly contains panel, Pilgrim's badge, and capital. Most of the art displayed at The Cloisters is in fact part of The Medieval Art department.

```{r}
met |>
  count(department) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  select(department, n) |> 
  rename("Department" = department, "Number of Objects" = n) |>
  knitr::kable(caption = "Top 3 Departments by Number of Objects")
```

```{r out.width='100%'}
met |> 
  count(department) |> 
  mutate(department = fct_reorder(department, n)) |> 
  plot_ly(x = ~department, y = ~n, color = ~department, type = "bar", colors = mypal) |>
  layout(title = 'Each department and their number of objects',
         xaxis = list(title = 'Department'), 
         yaxis = list(title = 'Number of Objects'),
         showlegend = FALSE)
```

The most objects can be found in the following departments: 1) Drawings and Prints; 2) European Sculpture and Decorative Arts; and 3) Asian Art.

```{r}
met |>
  filter(is_highlight == TRUE) |>
  count(department) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  select(department, n) |> 
  rename("Department" = department, "Number of Highlighted Objects" = n) |>
  knitr::kable(caption = "Top 3 Departments by Number of Highlighted Objects")
```

```{r out.width='100%'}
met |> 
  filter(is_highlight == TRUE) |>
  count(department) |> 
  mutate(department = fct_reorder(department, n)) |> 
  plot_ly(x = ~department, y = ~n, color = ~department, type = "bar", colors = mypal) |>
  layout(title = 'Each department and their number of highlighted objects',
         xaxis = list(title = 'Department'), 
         yaxis = list(title = 'Number of Highlighted Objects'),
         showlegend = FALSE)
```

The most highlighted objects can be found in the following departments: 1) The American Wing; 2) Asian Art; and 3) Costume Institute.

## Drawings and Prints

```{r}
met |>
  filter(department == "Drawings and Prints") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Drawings and Prints") |>
  count(object_name) |>
  filter(n > 760) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In Drawings and Prints, the most common objects are: 1) Print; 2) Drawing; and 3) Book.

## European Sculpture and Decorative Arts

```{r}
met |>
  filter(department == "European Sculpture and Decorative Arts") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "European Sculpture and Decorative Arts") |>
  count(object_name) |>
  filter(n > 89) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In European Sculpture and Decorative Arts, the most common objects are: 1) Piece; 2) Fragment; and 3) Vase.

## Photographs

```{r}
met |>
  filter(department == "Photographs") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Photographs") |>
  count(object_name) |>
  filter(n > 80) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In Photographs, the most common objects are: 1) Photograph; 2) Negative; and 3) Carte-de-visite.

## Asian Art

```{r}
met |>
  filter(department == "Asian Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Asian Art") |>
  count(object_name) |>
  filter(n > 142) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In Asian Art, the most common objects are: 1) Piece; 2) Print; and 3) Vase.

## Greek and Roman Art

```{r}
met |>
  filter(department == "Greek and Roman Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Greek and Roman Art") |>
  count(object_name) |>
  filter(n > 90) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In Greek and Roman Art, the most common objects are: 1) Kylix fragment; 2) Statue; and 3) Vase.

## Costume Institue

```{r}
met |>
  filter(department == "Costume Institute") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Costume Institute") |>
  count(object_name) |>
  filter(n > 90) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In Costume Institute, the most common objects are 1) Dress; 2) Ensemble; and 3) Evening dress.

## Egyptian Art

```{r}
met |>
  filter(department == "Egyptian Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Egyptian Art") |>
  count(object_name) |>
  filter(n > 54) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In Egyptian Art, the most common objects are: 1) Relief; 2) Scarab; and 3) Jar Label. 

## The American Wing

```{r}
met |>
  filter(department == "The American Wing") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "The American Wing") |>
  count(object_name) |>
  filter(n > 62) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar(aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In The American Wing, the most common objects are: 1) Drawing; 2) Painting; and 3) Watercolor.

## Islamic Art

```{r}
met |>
  filter(department == "Islamic Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Islamic Art") |>
  count(object_name) |>
  filter(n > 54) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In Islamic Art, the most common objects are: 1) Fragment; 2) Textile; and 3) Coin.

## Modern and Contemporary Art

```{r}
met |>
  filter(department == "Modern and Contemporary Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Modern and Contemporary Art") |>
  count(object_name) |>
  filter(n > 77) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In Modern and Contemporary Art, the most common objects are: 1) Drawing; 2) Painting; and 3) Textile.

## Arms and Armor

```{r}
met |>
  filter(department == "Arms and Armor") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Arms and Armor") |>
  count(object_name) |>
  filter(n > 28) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In Arms and Armor, the most common objects are: 1) Sword guard (Tsuba); 2) Knife handle (Kozuka); and 3) Arrowhead (Yanone).

## Arts of Africa, Oceania, and the Americas

```{r}
met |>
  filter(department == "Arts of Africa, Oceania, and the Americas") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Arts of Africa, Oceania, and the Americas") |>
  count(object_name) |>
  filter(n > 35) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In Arts of Africa, Oceania, and the Americas, the most common objects are: 1) Vase; 2) Figure; and 3) Mask.

## Medieval Art

```{r}
met |>
  filter(department == "Medieval Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Medieval Art") |>
  count(object_name) |>
  filter(n > 24) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In Medieval Art, the most common objects are: 1) Fragment; 2) Ostrakon; and 3) Brooch.

## Ancient Near Eastern Art

```{r}
met |>
  filter(department == "Ancient Near Eastern Art") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Ancient Near Eastern Art") |>
  count(object_name) |>
  filter(n > 25) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In Ancient Near Eastern Art, the most common objects are: 1) Stamp seal; 2) Cuneiform tablet; and 3) Cylinder seal.

## Musical Instruments

```{r}
met |>
  filter(department == "Musical Instruments") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Musical Instruments") |>
  count(object_name) |>
  filter(n > 9) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In Musical Instruments, the most common objects are: 1) Bell; 2) Pottery Whistle; and 3) Rattle.

## European Paintings

```{r}
met |>
  filter(department == "European Paintings") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "European Paintings") |>
  count(object_name) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In European Paintings, the most common objects are: 1) Painting; and 2) Drawing.

## Robert Lehman Collection

```{r}
met |>
  filter(department == "Robert Lehman Collection") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "Robert Lehman Collection") |>
  count(object_name) |>
  filter(n > 10) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In the Robert Lehman Collection, the most common objects are: 1) Drawing; 2) Frame; and 3) Painting.

## The Cloisters

```{r}
met |>
  filter(department == "The Cloisters") |>
  count(object_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 6) |> 
  arrange(desc(n)) |>
  rename("Object Name" = object_name, "Number of Objects" = n) |>
  select("Object Name", "Number of Objects") |> 
  knitr::kable(caption = "Most common objects")

met |> 
  filter(department == "The Cloisters") |>
  count(object_name) |>
  filter(n > 9) |>
  ggplot(aes(x = reorder(object_name, n, fill = object_name), y = n)) + 
  geom_bar( aes(fill = object_name), stat = "identity", show.legend = FALSE) + 
  labs(
    title = "Explore the most common objects",
    x = "Object Name",
    y = "Number of Objects",
    fill = "Object Name"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(values = wes_palette("AsteroidCity1"))
```

In The Cloisters, the most common objects are: 1) Panel, 2) Pilgrim's badge; and 3) Capital.
