---
title: "Final Project <br> Deliverable 1: Team Registration and Project Topic Proposal"
author: "**Team:** Jennifer Osei, Melike Aksoy, Emily Murphy, Aleya Khalifa, Andy Turner, Diana Hernandez <br>" 
date:  "**Date:** `r format(Sys.time(), '%A, %B %d, %Y %I:%M %p')`"
output: github_document
editor_options: 
  chunk_output_type: inline
---
### General Instructions: Deliverables & Submissions
Other than peer assessments, each deliverable will appear online (as e.g. a GH repo or youtube video). 
Links should be submitted via Courseworks by one team member (not necessarily the same person for each deliverable).

There should be one proposal per group, written collaboratively using .Rmd (rendering to a GH document) in a dedicated GitHub repo. This is intended to describe a project that is in the planning stages. Only one team member should submit this proposal via Canvas.<br> [Submission Completed xxxxxxxxx XX]

Please also submit (only once per team) a list of your team’s UNIs using this form. Doing so will help us keep track of teams.<br> [Submission Completed Mon. November 6, 2023 JO ]

# Deliverable 1: Team Registration and Project Topic Proposal 
First, you will define your teams and propose a project. <br>
This proposal should be a half-page to a page in length and include:

## 1.The group members (names and UNIs)
```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(kableExtra)

#Creating Tibble for Kable Table - Group Member Names & UNIs
our_team = tibble (Group_Member_Names = c("Jennifer Osei", "Melike Aksoy","Emily Murphy", "Aleya Khalifa", "Andy Turner", "Diana Hernandez"), 
                UNIs = c("jao2195", "mma2277", "erm2195", "ak4598", "ajt2206", "dmh2228"))

#Creating Neat Table, with Left Alignment for both columns.
knitr::kable(our_team, caption = "*Table 1: Team Members and UNIs*", align = "ll")

```

## 2. The tentative project title

**The Art of Data Science: Exploring the Origins The Met's Collections**


## 3. The motivation for this project

The Met is the largest museum in the United States as such it would take days of visits to see all the pieces of art on display. To help fight the sensory overload (and exposure to dry air) that comes with repeated visits, we will be analyzing the Met's collections. Breaking down artifacts by country and culture of origin, creating a timeline of Met artifacts, and creating visualizations worthy of the Met itself will all be part of the project. These data explorations and visualizations will provide Met visitors with a deeper understanding of its collections - both before and after their visits to the museum.

_Where does art come from in terms of culture, period, gender, and beyond?_

## 4. The intended final products

We will create a website with dashboard that hosts multiple data visualizations and a description of our analyses.

## 5. The anticipated data sources

[The Met Museum] (https://metmuseum.github.io/)

## 6. The planned analyses / visualizations / coding challenges

### Planned analyses

-   number of artefacts by dynasty and reign
-   number of artefacts by culture over time
-   trends in the counts of different types of art (e.g., painting, sculpture, etc.) acquired by the MET
-   medium of the art by gender of the artist, and whether that differs by highlighted and non-highlighted objects
-   relationship between an artwork being in the public domain and being highlighted
-   rivers depicted most frequently/rarely

### Visualizations

-   world map
-   sankey plot to visualize flows from where artefact originated and where the excavator was from
-   bar chart
-   timeline using line chart

### Coding challenges

-   working with almost string variables, some of which needed to be recoded
-   handling missing data when aggregating data by category
-   not all categories will pertain to all artefacts, like `reign`, since artefacts may be from more recent periods
-   working with such a large dataset, we'll have to decide how to filter especially when using dashboard


## 7. The planned timeline

Add:
-   cleaned dataset

```{r, echo=FALSE}
#Creating Tibble for Kable Table - Our Plan for Timeline
our_plan = tibble (Deliverable_Number = c(1:6) , Day = c("Friday", "Friday", "Saturday", "Saturday", "Saturday", "Thursday"),
                Date = c("November 10, 2023","November 17, 2023", "November 25, 2023", "December 2, 2023", "December 9, 2023","December 14, 2023") ,  
                               Time_Due = c("1:00pm", "TBD", "11:59pm", "11:59pm", "11:59pm", "10am - 11:20pm"), 
                               Description = c("Form a Team and Submit a Proposal", "Project Review Meeting", "Vizualizations Drafted", "Vizualizations Finalized", "Report | Webpage & Screencast | Peer Assessment ", "In Class Discussion of Final Projects"), 
                              Canvas_Submission = c("YES", "NO", "NO", "NO", "YES", "NO"), 
                               Type = c("Github Document", "Zoom Meeting", "Github Document", "Github Document", "Github Document | Website | Github Document", "NONE"),
                               Deliverable = c("Written Proposal Document", "NONE: Zoom Meeting", "Drafted Github Code and Visualizations", "Clean and Finished Github Code and Visualizations", "Written Report Giving Detailed Project Description | Webpage Overview of Project with Short Explanatory Video (Published Online) | Brief Assessment of Your Teammates Contributions (as a Short Document)", "NONE: Enjoy Hearing about Projects! (and also get Hex Stickers)"))

#Creating Neat Table, with visually appropriate alignments for all columns.
knitr::kable(our_plan, caption = "*Table 2: Team Project Timeline*", align = "cllclcll")
```



