---
title: "Final Project - Deliverable 1 - Team Registration and Project Topic Proposal"
author: "Jennifer Osei, Melike Aksoy, Emily Murphy, Aleya Khalifa, Andy Turner"
date: "2023-11-06"
output: github_document
---
##########################################################################
### Deliverable 1 - Team Registration and Project Topic Proposal 
##########################################################################

#### Deliverables (General)
#### Submissions

Other than peer assessments, each deliverable will appear online (as e.g. a GH repo or youtube video). Links should be submitted via Courseworks by one team member (not necessarily the same person for each deliverable).

#### Team registration and proposal
First, you will define your teams and propose a project. 
This proposal should be a half-page to a page in length and include:

1. The group members (names and UNIs)

```{r, echo = FALSE, message = FALSE}
library(tidyverse)

#Creating Tibble for Kable Table.
our_team = tibble (Group_Members = c("Jennifer Osei", "Melike Aksoy","Emily Murphy", "Aleya Khalifa", "Andy Turner"), 
                UNIs = c("jao2195", "mma2277", "erm2195", "ak4598", "ajt2206"))

#Creating Neat Table, with Left Alignment for both columns.
knitr::kable(our_team, caption = "Table 1: Team Members and UNIs ", align = "ll")

```

2. The tentative project title

3. The motivation for this project

4. The intended final products

5. The anticipated data sources

6. The planned analyses / visualizations / coding challenges


7. The planned timeline
```{r, echo=FALSE}
our_plan = tibble (Deliverable_Number = c(1:4) , Day = c("Friday", "Friday", "Saturday", "Thursday"),
                Date = c("November 10, 2023","November 17, 2023","December 9, 2023","December 14, 2023") ,  
                               Time_Due = c("1:00pm", "TBD", "11:59pm", "10am - 11:20pm"), 
                               Description = c("Form a Team and Submit a Proposal", "Project Review Meeting", "Report| Webpage & Screencast | Peer Assessment ", "In Class Discussion of Final Projects"), 
                              Canvas_Submission = c("YES", "NO", "YES", "NO"), 
                               Type = c("Github Document", "Zoom Meeting", "Github Document | Website | Github Document", "NONE"),
                               Deliverable = c("Written Proposal Document", "NONE: Zoom Meeting", "Written Report Giving Detailed Project Description | Webpage Overview of Project with Short Explanatory Video (Published Online) | Brief Assessment of Your Teammates Contributions (as a Short Document)", "NONE: Enjoy Hearing about Projects! (and also get Hex Stickers)"))

knitr::kable(our_plan, caption = "Table 2: Team Project Timeline", align = "cllclcll")
```

There should be one proposal per group, written collaboratively using .Rmd (rendering to a GH document) in a dedicated GitHub repo. This is intended to describe a project that is in the planning stages. Only one team member should submit this proposal via Canvas. [Submission Completed xxxxxxxxx XX]

Please also submit (only once per team) a list of your team’s UNIs using this form. Doing so will help us keep track of teams.[Submission Completed Mon. November 6, 2023 JO]

