---
title: "Final Project <br> Deliverable 1: Team Registration and Project Topic Proposal"
author: "**Team:** Jennifer Osei, Melike Aksoy, Emily Murphy, Aleya Khalifa, Andy Turner <br>" 
date:  "**Date:** `r format(Sys.time(), '%A, %B %d, %Y %I:%M %p')`"
output: github_document
editor_options: 
  chunk_output_type: inline
---
### General Instructions: Deliverables & Submissions
Other than peer assessments, each deliverable will appear online (as e.g. a GH repo or youtube video). 
Links should be submitted via Courseworks by one team member (not necessarily the same person for each deliverable).

There should be one proposal per group, written collaboratively using .Rmd (rendering to a GH document) in a dedicated GitHub repo. This is intended to describe a project that is in the planning stages. Only one team member should submit this proposal via Canvas.<br> [Submission Completed xxxxxxxxx XX]

Please also submit (only once per team) a list of your team’s UNIs using this form. Doing so will help us keep track of teams.<br> [Submission Completed Mon. November 6, 2023 JO ]

### Deliverable 1: Team Registration and Project Topic Proposal 
First, you will define your teams and propose a project. <br>
This proposal should be a half-page to a page in length and include:

**1.The group members (names and UNIs)**
```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(kableExtra)

#Creating Tibble for Kable Table - Group Member Names & UNIs
our_team = tibble (Group_Member_Names = c("Jennifer Osei", "Melike Aksoy","Emily Murphy", "Aleya Khalifa", "Andy Turner"), 
                UNIs = c("jao2195", "mma2277", "erm2195", "ak4598", "ajt2206"))

#Creating Neat Table, with Left Alignment for both columns.
knitr::kable(our_team, caption = "*Table 1: Team Members and UNIs*", align = "ll")

```

**2. The tentative project title**

**3. The motivation for this project**

**4. The intended final products**

**5. The anticipated data sources**

**6. The planned analyses / visualizations / coding challenges**

**7. The planned timeline**
```{r, echo=FALSE}
#Creating Tibble for Kable Table - Our Plan for Timeline
our_plan = tibble (Deliverable_Number = c(1:4) , Day = c("Friday", "Friday", "Saturday", "Thursday"),
                Date = c("November 10, 2023","November 17, 2023","December 9, 2023","December 14, 2023") ,  
                               Time_Due = c("1:00pm", "TBD", "11:59pm", "10am - 11:20pm"), 
                               Description = c("Form a Team and Submit a Proposal", "Project Review Meeting", "Report| Webpage & Screencast | Peer   Assessment ", "In Class Discussion of Final Projects"), 
                              Canvas_Submission = c("YES", "NO", "YES", "NO"), 
                               Type = c("Github Document", "Zoom Meeting", "Github Document | Website | Github Document", "NONE"),
                               Deliverable = c("Written Proposal Document", "NONE: Zoom Meeting", "Written Report Giving Detailed Project Description | Webpage Overview of Project with Short Explanatory Video (Published Online) | Brief Assessment of Your Teammates Contributions (as a Short Document)", "NONE: Enjoy Hearing about Projects! (and also get Hex Stickers)"))

#Creating Neat Table, with visually appropriate alignments for all columns.
knitr::kable(our_plan, caption = "*Table 2: Team Project Timeline*", align = "cllclcll")
```



