---
title: "Exhibit D: Discovering Inside The Met"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    navbar:
      - {icon: "fa-home", href: "./index.html", align: right }
---
```{r, echo=FALSE, message=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(sf)
library(shiny)
library(rnaturalearth)
library(rsconnect)
library(dplyr)

```

```{r, echo=FALSE, warning=FALSE}
load("data/met.RData")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
met_country <- met |> 
mutate(country = case_when(
    country == "Central Turkey" ~ "Turkey",
    country == "USA" ~ "United States", 
    country == "Iran(Persia)" ~ "Iran", 
    country == "Ivory Coast" ~ "Cote d'Ivoire", 
    country == "iran" ~ "Iran", 
    country == "Eastern India" ~ "India",
    country == "Byzantine Egypt" ~ "Egypt",
    country == "Western Australia" ~ "Australia",
    country == "England" ~ "United Kingdom",
    country == "England|England" ~ "United Kingdom",
    country == "Crotia(former Yugoslavia)" ~"Crotia",
    country == "Western France" ~ "France", 
    country == "Southern Netherlands" ~ "Netherlands",
    country == "Southern Netherland" ~ "Netherlands", 
    country == "Scotland" ~ "United Kingdom",
    country == "Republic of Congo" ~ "Congo", 
    country == "Republic of Cameroon" ~ "Cameroon",
    country == "Republic of Costa Rica" ~ "Costa Rica",
    country == "Republic of Guinea-Bissau" ~ "Guinea-Bissau",
    country == "Republic of the Marshall Islands" ~ "Marshall Isl",
    country == "Republic of Guinea-Bissau" ~ "Guinea-Bissau",
    country == "Republic of Benin" ~ "Benin",
    country == "Northern Iran"  ~"Iran",
    country == "Northwestern Iran"  ~"Iran",
    country == "Northwest Iran"  ~"Iran",
    country == "Northwestern Iran" ~"Iran",
    country == "Northern India" ~ "India",
    country == "Nothern France" ~ "France", 
    TRUE ~ as.character(country)
  ), 
  country = str_replace(country, "present-day ", ""))

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
object_counts <- met |> 
  group_by(country, object_name, department) |> 
  summarise(n_objects = n()) |> 
  group_by(country,department) |> 
  summarise(total_objects = sum(n_objects, na.rm = TRUE))


world <- ne_countries(scale = "medium", returnclass = "sf")

world <- left_join(world, object_counts, by = c("name" = "country"))
world2 <- left_join(object_counts, world, by = c("country" = "name"))

world2 <- world2 |> 
  filter(is.na(scalerank))
```
HELLO! Please select the floor you want to tour to see different departments of the Met. This page includes the information about department locations and number of total objects in each department. If you want to compare the number of object between different departments, check out our bar plots. When you want to see the total number of objects from the department that you are interested in, please click on the location pin. Enjoy!

Column {data-width=100%}
-----------------------------------------------------------------------
Column {.tabset .tabset-fade}
-------------------------------------
### First Floor

```{r, echo=FALSE}
library(leaflet)

met_departments <- data.frame(
  department_name = c("The American Wing", "European Sculpture and Decorative Arts", "Modern and Contemporary Art", "Egyptian Art", "Greek and Roman Art", "Medieval Art", "Arms and Armor"),
  lat = c(40.780611, 40.779861, 40.778778, 40.780167, 40.778444, 40.779583, 40.780083),
  lng = c(-73.963361, -73.963250, -73.964667, -73.962167, -73.963306, -73.963694, -73.963000),
  department_info = c("1844", "4256", "1478", "2875", "3420", "764", "1351")
)

firstfl <- leaflet() %>%
  addTiles() %>%
  setView(lng = -73.963402, lat = 40.779434, zoom = 15)

for (i in seq_len(nrow(met_departments))) {
  firstfl <- firstfl %>%
    addMarkers(
      lat = met_departments$lat[i],
      lng = met_departments$lng[i],
      popup = paste("Department: ", met_departments$department_name[i], "<br>",
                    "Number of Objects: ", met_departments$department_info[i]),
      options = popupOptions(
        maxWidth = 300,
        closeOnClick = TRUE
      )
    )
}

firstfl
```

### First Floor Barplot

```{r, echo=FALSE}
library(leaflet)
library(dplyr)
library(plotly)

met_departments <- data.frame(
  department_name = c("The American Wing", "European Sculpture and Decorative Arts", "Modern and Contemporary Art", "Egyptian Art", "Greek and Roman Art", "Medieval Art", "Arms and Armor"),
  lat = c(40.780611, 40.779861, 40.778778, 40.780167, 40.778444, 40.779583, 40.780083),
  lng = c(-73.963361, -73.963250, -73.964667, -73.962167, -73.963306, -73.963694, -73.963000),
  department_info = c("1844", "4256", "1478", "2875", "3420", "764", "1351")
)

met_departments <- met_departments %>%
  mutate(Floor = case_when(
    grepl("first floor", tolower(department_name)) ~ "First Floor",
    grepl("second floor", tolower(department_name)) ~ "Second Floor",
    grepl("the cloisters", tolower(department_name)) ~ "The Cloisters",
    TRUE ~ "Other"
  ))

barplot_data <- object_counts %>%
  filter(department %in% met_departments$department_name)


bar_plot <- plot_ly(barplot_data, x = ~department, y = ~total_objects, type = "bar") %>%
  layout(
    title = "First Floor",
    xaxis = list(title = "Department"),
    yaxis = list(title = "Number of Objects")
  )

# Show the plot
bar_plot

```

### Second Floor

```{r, echo=FALSE}
library(leaflet)


met_departments <- data.frame(
  department_name = c("Islamic Art", "Ancient Near Eastern Art", "Drawings and Prints", "Photographs", "Musical Instruments", "Asian Art", "European Paintings", "The American Wing"),
  lat = c(40.778222, 40.778611, 40.778778, 40.778833, 40.780056, 40.779694, 40.779861, 40.780250),
  lng = c(-73.963500, -73.963083, -73.963639,-73.963833,-73.963056, -73.962472,  -73.963556, -73.963361),
  department_info = c("1599", "618", "17.146K", "3663", "506", "3773", "286", "1844" )
)


secondfl <- leaflet() %>%
  addTiles() %>%
  setView(lng = -73.963402, lat = 40.779434, zoom = 15)


for (i in seq_len(nrow(met_departments))) {
  secondfl <- secondfl %>%
    addMarkers(
      lat = met_departments$lat[i],
      lng = met_departments$lng[i],
      popup = paste("Department: ", met_departments$department_name[i], "<br>",
                    "Number of Objects: ", met_departments$department_info[i]),
      options = popupOptions(
        maxWidth = 300,
        closeOnClick = TRUE
      )
    )
}

secondfl
```

### Second Floor Barplot

```{r, echo=FALSE}
library(leaflet)
library(dplyr)
library(plotly)


met_departments <- data.frame(
  department_name = c("Islamic Art", "Ancient Near Eastern Art", "Drawings and Prints", "Photographs", "Musical Instruments", "Asian Art", "European Paintings", "American Wing"),
  lat = c(40.778222, 40.778611, 40.778778, 40.778833, 40.780056, 40.779694, 40.779861, 40.780250),
  lng = c(-73.963500, -73.963083, -73.963639, -73.963833, -73.963056, -73.962472, -73.963556, -73.963361),
   department_info = c("1599", "618", "17.146K", "3663", "506", "3773", "286", "1844" )
)

met_departments <- met_departments %>%
  mutate(Floor = case_when(
    grepl("first floor", tolower(department_name)) ~ "First Floor",
    grepl("second floor", tolower(department_name)) ~ "Second Floor",
    grepl("the cloisters", tolower(department_name)) ~ "The Cloisters",
    TRUE ~ "Other"
  ))

barplot_data <- object_counts %>%
  filter(department %in% met_departments$department_name)

second <- plot_ly(barplot_data, x = ~department, y = ~total_objects, type = "bar") %>%
  layout(
    title = "Second Floor",
    xaxis = list(title = "Department"),
    yaxis = list(title = "Number of Objects")
  )

# Show the plot
second


```

### Floor G

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(magrittr)
library(leaflet)

met_departments <- data.frame(
  department_name = c("Robert Lehman Collection", "Costume Institute"),
  lat = c(40.77984, 40.780194),
  lng = c(-73.96422, -73.961944),
  department_info = c("241", "3226")
)


gfl <- leaflet() %>%
  addTiles() %>%
  setView(lng = -73.963402, lat = 40.779434, zoom = 15)

# Add markers for each department
for (i in seq_len(nrow(met_departments))) {
  gfl <- gfl |> 
    addMarkers(
      lat = met_departments$lat[i],
      lng = met_departments$lng[i],
      popup = paste("Department: ", met_departments$department_name[i], "<br>",
                    "Number of Objects: ", met_departments$department_info[i]),
      options = popupOptions(
        maxWidth = 300,
        closeOnClick = TRUE
      )
    )
}

gfl
```

### Floor G Barplot

```{r, echo=FALSE}
library(leaflet)
library(dplyr)
library(plotly)


met_departments <- data.frame(
  department_name = c("Robert Lehman Collection", "Costume Institute"),
  lat = c(40.77984, 40.780194),
  lng = c(-73.96422, -73.961944),
  department_info = c("241", "3226")
)


met_departments <- met_departments %>%
  mutate(Floor = case_when(
    grepl("first floor", tolower(department_name)) ~ "First Floor",
    grepl("second floor", tolower(department_name)) ~ "Second Floor",
    grepl("floor g", tolower(department_name)) ~ "Floor G or B1",
    grepl("the cloisters", tolower(department_name)) ~ "The Cloisters",
    TRUE ~ "Other"
  ))

barplot_data <- object_counts %>%
  filter(department %in% met_departments$department_name)

plotg <- plot_ly(barplot_data, x = ~department, y = ~total_objects, type = "bar") %>%
  layout(
    title = "Floor G",
    xaxis = list(title = "Department"),
    yaxis = list(title = "Number of Objects")
  )


plotg


```


### The Cloisters

```{r, echo=FALSE}
met_departments <- data.frame(
  department_name = c("The Cloisters"),
  lat = c(40.8649),
  lng = c(-73.9317),
  department_info = c("218")
)


cloisters <- leaflet() %>%
  addTiles() %>%
  setView(lng = -73.9317, lat = 40.8649, zoom = 15)


for (i in seq_len(nrow(met_departments))) {
  cloisters <- cloisters %>%
    addMarkers(
      lat = met_departments$lat[i],
      lng = met_departments$lng[i],
      popup = paste("Department: ", met_departments$department_name[i], "<br>",
                    "Number of Objects: ", met_departments$department_info[i]),
      options = popupOptions(
        maxWidth = 300,
        closeOnClick = TRUE
      )
    )
}

cloisters

```


















