---
title: "Exhibition A: The Data"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
---

```{r include = FALSE}
load("data/met.RData")
```

# **Data Source**

The Met offers open access to data of its collection. It can be found [here](https://github.com/metmuseum/openaccess).

# **Data Cleaning**

* The Met dataset consists of over 400,000 observations. A dataset of this size was far too big to handle.

* We took a look at missing data to decide how to subset the dataset into a smaller, more manageable size. The variables `object_name` and `accession_year` were complete. From that information, we took a random sample of 10% of the data, creating our final dataset of over 40,000 observations.

```{r echo = FALSE}
sapply(met, function(x) sum(is.na(x)))
```

Based on the missing data, we chose the following variables to work with: 

* `is_highlight`: When "true" indicates a popular and important artwork in the collection
* `department`: Indicates The Met's curatorial department responsible for the artwork
* `accession_year`: Year the artwork was acquired
* `culture`: Information about the culture, or people from which an object was created
* `object_name`: Describes the physical type of the object
* `country`: Country where the artwork was created or found

